Flexible Scientific Data Management for Plant Phenomics Research

### 2013-04-15 s4biodiv2013/Rebuttals.txt

 *****

"any OWL object property that has been defined to link from image acquisition runs to images can be used to define the purpose of an image" - are you saying that images are properties of image acquisition runs?  and that the link between an image acquisition process, and its resulting image, defines the purpose of the image?  How so??

 *****

 Rebuttal : Rewrote this sentence so it refers to provenance, not properties.

@@

Overall, I thought the manuscript was unnecessarily opaque, didn't emphasise the primary themes of "biodiversity" and "semantics", and over-emphasised many other aspects of their phenotype acquisition and processing workflow.  It's not a bad manuscript, at all, and is likely very well-suited for submission elsewhere (if made slighly less "jargony")!  However, I don't see the fit with this meeting, unless it is extensively re-written.

 *****

 Rebuttal : We feel that the reviewer did not recognise the attempt to provide a high level view of the integrated PODD and PlantScan system and how it is being used by HRPPC to process plant phenomics data (Section 2). Plant phenomics is a legitimate subset of biodiversity. It highlights differences between, and inside, multiple plant species based on feature comparisons. This paper provides a description of the high level use of ontologies to structure and enrich a semantic data model based on RDF and OWL. OWL is used in PODD for both syntactic validation and sparse semantic enrichment purposes.

 The reviewer requests that the manuscript use less jargon, while also requiring more detail about what ontologies are in use (See Figure and how they are being practically used, which entails using more jargon related to those specific ontologies.

### 2013-04-15 s4biodiv2013/PODD-S4BIODIV-Submission.tex

OWL is used to determine whether projects are both internally consistent, with
all objects having an explicit RDF type, and whether they are consistent with
the ontologies that they import. 
%The main point that PODD focuses on for
%validation is determining that mappings are consistent with the basic PODD
%predicates and classes, so that they can be used to render both static HTML
%pages and provide HTML based editing facilities. 
For example, any OWL object
property that has been defined to link from image acquisition runs to images can
be used to define the purpose of an image. This may include any combination of
the defined properties, without requiring all of the properties to be used.
% The parent object types and properties used by PODD to establish basic ground
% rules for rendering and validation are defined in a small base schema ontology.
General scientific properties and phenotype specific properties are defined
in optional extension ontologies as illustrated in Figure~\ref{poddontologies}.
These are used by scientists to annotate their projects with concepts specific 
to their field, without requiring other scientists using the same PODD installation 
to use phenotype properties to annotate their projects.

>>>>

OWL is used to determine whether projects are both internally consistent, with
all objects having an explicit RDF type, and whether they are consistent with
the ontologies that they import. 
%The main point that PODD focuses on for
%validation is determining that mappings are consistent with the basic PODD
%predicates and classes, so that they can be used to render both static HTML
%pages and provide HTML based editing facilities. 
For example, any OWL object property that has been defined to link from image 
acquisition runs to images defines the provenance of an image.

%This may include 
%any combination of the defined properties, without requiring all of the properties 
%to be used.
% The parent object types and properties used by PODD to establish basic ground
% rules for rendering and validation are defined in a small base schema ontology.

General scientific properties and phenotype specific properties are defined
in optional extension ontologies as illustrated in Figure~\ref{poddontologies}.
These are used by scientists to annotate their projects with concepts specific 
to their field, without requiring other scientists using the same PODD installation 
to use phenotype properties to annotate their projects.
